---
title: "HW1"
author: "배현주"
date: "9/23/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment=NA)
rm(list=ls())
```

## 1. Age distribution of American boys named Joseph

### Load libraries
```{r cars, message=FALSE}
library(babynames)
library(mdsr)
library(dplyr)
library(Hmisc)
library(scales)
library(ggplot2)
```
<br />

### Load dataset
```{r}
baby_data <- make_babynames_dist()
str(baby_data)
```
<br />

### Plot
1. Filter the data and find the median year and number of Joseph alive.
```{r}
joseph <- filter(baby_data, name == "Joseph", sex == "M")
alive_n.median <- with(joseph, wtd.quantile(year, est_alive_today, prob=0.5))
alive_n.median
```
> The median number of living still Joseph is 20847.19 and the birth of year is 1975.

2. Plot the number of Josephs born each year
```{r}
joseph_num <- ggplot(data=joseph) +
  geom_line(mapping = aes(x=year, y=n/1000)) +
  labs(title = "Age Distribution of American Boys Named Joseph",
       subtitle = "By year of birth") +
  ylab("") +
  coord_cartesian(ylim=c(0, 40), expand=TRUE) +
  geom_text(x = 1940, y = 34, label = "Number of Josephs\nborn each year")
joseph_num
```

3. Plot the number of Joseph alive 
```{r}
joseph_num <- joseph_num +
  geom_bar(mapping = aes(x=year, y=est_alive_today/1000), 
           stat="identity", fill="skyblue3", width=0.5) +
  geom_text(x = 1915, y = 15, 
            label = "Number of Josephs\nborn each year\nestimated to be alive\non 1/1/2014",
            colour = "skyblue3")
joseph_num
```

4. Highlight the median number of Joseph alive
```{r}
joseph_num <- joseph_num +
  geom_bar(mapping = aes(x=alive_n.median, y=ifelse(year == alive_n.median, est_alive_today/1000, 0)), 
           stat="identity", fill="dodgerblue3", width=0.7) +
  geom_text(x = 1990, y = 37,
            label = "The median living Joseph\nis 37 years old",
            colour = "dodgerblue3") +
  geom_curve(x = 1990, xend = 1975, y = 34, yend = 24,
             arrow = arrow(length = unit(0.3,"cm")), curvature = 0.5) + ylim(0, 42)
joseph_num
```


## 2. Median ages for males with 25 most common names
### Load datasets
```{r}
rm(list=ls())
baby_data <- make_babynames_dist()
colnames(baby_data)
```

1. Filter the 25 most common names
```{r}
male <- baby_data %>% filter(sex == "M")
top25_male <- male %>%
  group_by(name) %>%
  summarise(N=sum(n)) %>%
  arrange(desc(N)) %>%
  head(25)

male <- male %>%
  filter(name %in% top25_male$name)
```


2. Make variables of Q1, median, Q3 age
```{r}
male_quant <- male %>%
  group_by(name) %>%
  summarise(q1_age = wtd.quantile(age_today, est_alive_today, probs = 0.25),
            med_age = wtd.quantile(age_today, est_alive_today, probs = 0.5),
            q3_age = wtd.quantile(age_today, est_alive_today, probs = 0.75))
```
<br />

### Plot
1. Make the background of the plot and flip the coordinate
```{r}
top25_male_plot <- ggplot(male_quant, aes(x = reorder(name, - med_age), y = med_age)) +
  xlab(NULL) +
  ylab(NULL) +
  labs(title = "Median Ages For Males with the 25 Most Common Names",
          subtitle = "Among Americans estimated to be alive as of Jan. 1, 2014") + 
    coord_flip()
top25_male_plot
```

2. Add Q1 - Q3 boxplot to the plot
```{r}
top25_male_plot <- top25_male_plot +
  geom_linerange(aes(ymin = q1_age, ymax = q3_age),
                 color = "skyblue3", size = 8, alpha = 0.8)
top25_male_plot
```

3. Add median point
```{r}
top25_male_plot <- top25_male_plot +
  geom_point(fill = "#ed3324", color = "white", size = 3, shape = 21)
top25_male_plot
```

4. Add text
```{r}
top25_male_plot <- top25_male_plot +
  geom_point(aes(y = 55, x = 24), fill = "#ed3324", colour = "white",
             size = 3, shape = 21) +
  geom_text(aes(y = 58, x = 24, label = "median")) +
  geom_text(aes(y = 28, x = 17, label = "25th")) +
  geom_text(aes(y = 49, x = 17, label = "75th percentile")) +
  geom_point(aes(y = 25, x = 17), shape = 17) +
  geom_point(aes(y = 55, x = 17), shape = 17)
top25_male_plot
```

5. Change the background and y lab
```{r}
top25_male_plot <- top25_male_plot + 
  theme(plot.background = element_rect(fill = "grey88"),
        panel.background = element_rect(fill = "grey88"),
        panel.grid.major.x = element_line(colour = "black", linetype = "dotted"),
        panel.grid.major.y = element_blank()) +
  scale_y_continuous(minor_breaks = seq(20, 60, 10),
                     breaks = seq(20, 60, 10),
                     labels = c('20 years old', '30', '40', '50', '60'),
                     position = 'right')
top25_male_plot
```



